Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-22 paper/main.tex
spivak fiber

\begin{definition} The \textcolor{fiber}{fiber space} \dfiberc\ is a topological space such that for every $\dbasepoint \in \dbase$, the fiber over that point is isomorphic to the preimage of that point $\dfiber_{\dbasepoint} \cong \pi^{-1}(\{\dbasepoint\})$. All fibers $\dfiber_{\dbasepoint}$ are homeomorphic to each other \cite{spanier1989algebraic, hatcherAlgebraicTopology2002}
\end{definition}
\note{intuition about fiber + spivak}

@@

\subsection{Data Domain}
We model data as sections of a fiber bundle $(\dtotal, \pi, \dbase, \dfiber)$. We encode the continuity of the data as the \textcolor{base}{base space} $\dbase$. We model the data as the section \dsection\ because, as described in \autoref{sec:related-work:fiber-bundles}, the section is the map from the indexing space \dbase\ to the space of possible data values \dfiber. We adopt Spivak's formulation of the fiber as a (column name, data domain) simple schema \cite{spivakSIMPLICIALDATABASES,spivakDatabasesAreCategories2010}. Spivak formally maps column names and field types to the set of values associated with the field type, for example $\mathbb{R}$ for a \texttt{float} column named \textit{temperature}. This allows for field based selection of values, while inclusion allows for continuity (index) based selections.

>>>>

\begin{definition} The \textcolor{fiber}{fiber space} \dfiberc\ is a topological space such that for every $\dbasepoint \in \dbase$, the fiber over that point is isomorphic to the preimage of that point $\dfiber_{\dbasepoint} \cong \pi^{-1}(\{\dbasepoint\})$. All fibers $\dfiber_{\dbasepoint}$ are homeomorphic to each other \cite{spanier1989algebraic, hatcherAlgebraicTopology2002}
\end{definition}

The fibers can be thought of as encapsulating data types according to Spivak, who proposes that databases can be represented as fiber bundles \cite{spivakSIMPLICIALDATABASES,spivakDatabasesAreCategories2010}. Spivak formulates the fiber as a (field name, data domain) simple schema where field names and field types can be formally mapped to the set of values associated with the field type, for example $\mathbb{R}$ for a \texttt{float} column named \textit{temperature}.

@@

\subsection{Data Domain}
We model data as sections of a fiber bundle $(\dtotal, \pi, \dbase, \dfiber)$. We encode the continuity of the data as the \textcolor{base}{base space} $\dbase$. We model the data as the section \dsection\ because, as described in \autoref{sec:related-work:fiber-bundles}, the section is the map from the indexing space \dbase\ to the space of possible data values \dfiber.
